Issues with Dynamical Measurements Across the Disk

### 2019-03-18 paper/ms.tex
Add dJz fun Jz plot to paper

@@

>>>>

\begin{figure}
\plotone{fig/schmactions_many_orbits_Jz_fun.pdf}
\caption{The fractional error in $J_z$ as a function of $J_z$ for a few
different offsets in $z$. We show this for a $z$ offset of $10, 50, 100\,\pc$
(red, cyan, green respectively). As before, the error ($\Delta J_z$) is the
95\uth{} minus 5\uth{} percentile of the distribution of observed $J_z$ values
over the course of the orbit. There are large errors for thin-disk like orbits
($J_z \sim 0.5\,\actunit$), even for a small midplane offset of $10\,\pc$. }
\label{fig:dJz_fun_Jz}
\end{figure}

@@

To further understand the effect of the midplane error, we also plot the
fractional error in $J_z$ as a function of $J_z$ for $z$ offsets of $10, 50,
100\,\pc$ (red, cyan, green, respectively) in Figure~\ref{fig:dJz_fun_Jz}. For
a thin disk-like orbit ($J_z\sim0.5\,\actunit$), even a $10\,\pc$ offset in
$z$ is enough to induce a $\sim50\%$ error in $J_z$. For larger values of
$J_z$, the fractional errors are suppressed, with the situation becoming worse
the greater the $z$ offset is.
